\plaintitle

### 2016-05-20 paper/paper.tex
Little changes
I don't remember

\section{Goal and Target Audience}\label{sec:goal} 
The visualization's goal can be best summarized by the following sentence: ``Why
did a certain NBA-team win the Championship?'' The visualization focuses on exposing relations between team
performance and their player roster over several years. It allows users to find
explanations for major improvements and declines in team performance.  The
visualization allows exploration of NBA data by lay persons.  More specifically,
the visualization does not focus on premade explanations for phenomenons
visible in the NBA data. By providing easy and intuitive access to the data, the
visualization allows users to draw their own conclusions. The visualization's
target audience are lay persons. Specifically, fans of NBA are the core of our
target audience. This means the visualization assumes most common basketball
terms are known to the audience and does not provide basic terminology
explanations. 
< We also give basic insights in why a statistic changes (arrow views)
we try to help them explore patters and trigger them for questions
Do we create awareness?
>

@@

<Explain that this complies with the infovis seeking mantra: Overview, zoom&filter, details on demand
play-off view = overview
statistics view= details on demand
Talk about th organization of the 3 views + the choice for a tiled approach
- Each page is a 'tile' that we force with fixed scrolling
- Use of the keyboard is possible (space bar to scroll + arrows, arrows for timeline)
- This papers are usefulle to refer to
http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado_MultipleViews_AVI00.pdf
http://www.interactiondesign.us/courses/2011_AD690/PDFs/Shneiderman_1996.pdf
http://www2.parc.com/istl/groups/uir/publications/items/UIR-1986-02-Mackinlay-TOG-Automating.pdf
>

@@

@@

\subsubsection{Arrow section of selected statistic}
This section illustrates a change for a chosen statistic for the selected team compared with the season before. This should give a visitor more insight into why a statistic changed over time. The selected team is represented by a circle in the same way as explained in the play-off view. The change for a statistic is represented by three arrows:
\begin{itemize}
    \item Arrow on the left pointing towards the circle: indicating the influence of players who joined the team (team member current season, not previous season)
    \item Arrow on the right of the circle: indicating how the team inherent changed (team member this season and previous season)
    \item Arrow on the left pointing away from the circle: indicating the influence of players who left the team (team member previous season, not current season)
\end{itemize}
<figure of the statistics view>
The shirts next to the arrows are the shirts of players that had the biggest 
contribution to that arrow. Note that these shirts don't change in size. The box on 
the right enables the user to change between 
statistics. Next to that it informs the user of which statistic has been chosen. When 
the user hits the circle in the middle representing the teams, he is guided 
to the team view. This view will be explained in more detail in the next section.
<filtering: 
- time & team
- based on exploration (small multiples)
- dynamically: changes impact multiple parts>

\subsubsection{Small multiples of different statistics}
Below the arrow section small multiples are shown of multiple statistics over time. 
The line charts enables a user to identify peaks or drops that possibly influenced the 
outcome of a team is this season, following seasons or previous seasons. A user interacts with the visualization by shifting the bar indicating the current year displayed. By doing this the view gets updated and the user can see the impact on the team in the context section and why the statistic changes in the arrow section. An alternative to scroll through time is to use the timeline at the bottom of the page.
<this vis helps us comparre statistics over time and relations between them
eg. srs score & play-off ranking>

@@

\section{Possible improvements}
As with most projects, the result is never 'finished', meaning that there are always improvements
possible but due to timing or resource constraints the haven't all been implemented. In what 
follows, we suggest a number of features that might improve the visualization:
\begin{itemize}
    \item Smooth transitions between states could improve the user experience. For example when changing
    year, a transformation of the arrow in the statistics view would help the user see a difference between years.
    At the moment the arrows change at the blink of an eye, making it difficult for us humans with a short term memory
    to make the comparison.
    \item To further support our short term memory we could also 'save' the previous state. Eg. in the field view we could
    visualize ghost shirts to indicate which players left the team or position and highlight players that joined the team. 
    This would help the user see how the team changes over time.
    \item At the moment no attention has been payed to the process & provenance of the exploration. A user thus needs to 
    memorize his action to be able to share or reproduce his actions. This could be improved by adding URL parameters. This
    way a user at least can share or save a state of an analysis. One step further is to provide a play-feature. The visitor could 
    them share his exploration and replay it. A simple implemention would ask the visitor for a start date and an end date and
    would then 'play' the changes of a particular team and characteristic over time.
    \item We could support users further in exploring for patterns by focussing more on comparisons. We could integrate a view 
    where a visitor is able to compare two teams in the same year, or in two different years.
\end{itemize}

>>>>

\section{Goal and Target Audience}\label{sec:goal} 
The visualization's goal can be best summarized by the following sentence:
``Why did a certain NBA-team win the Championship?'' The visualization focuses
on exposing relations between team performance and their player roster over
several years. It allows users to find explanations for major improvements and
declines in team performance.  The visualization allows exploration of NBA data
by lay persons.  More specifically, the visualization does not focus on premade
explanations for phenomenons visible in the NBA data. By providing easy and
intuitive access to the data, the visualization allows users to draw their own
conclusions. The visualization's target audience are lay persons. Specifically,
fans of NBA are the core of our target audience. This means the visualization
assumes most common basketball terms are known to the audience and does not
provide basic terminology explanations.

< We also give basic insights in why a
statistic changes (arrow views) we try to help them explore patters and trigger
them for questions Do we create awareness?  >

@@

<Explain that this complies with the infovis seeking mantra: Overview, zoom\&filter, details on demand
play-off view = overview
statistics view= details on demand
Talk about th organization of the 3 views + the choice for a tiled approach
- Each page is a 'tile' that we force with fixed scrolling
- Use of the keyboard is possible (space bar to scroll + arrows, arrows for timeline)
- This papers are usefulle to refer to
http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado\_MultipleViews\_AVI00.pdf
http://www.interactiondesign.us/courses/2011\_AD690/PDFs/Shneiderman\_1996.pdf
http://www2.parc.com/istl/groups/uir/publications/items/UIR-1986-02-Mackinlay-TOG-Automating.pdf
>

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/presidentcandidatesvisualization}
  \caption{The path of president candidates in their road to become president.}~\label{fig:whitehousepath}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/playoffviewfirstdesign}
  \caption{First design of the play-off view.}~\label{fig:firstdesignplayoffview}
\end{figure}

\begin{figure}
\centering
  \missingfigure{}
%  \includegraphics[width=0.9\columnwidth]{figures/playoffviewfirstimplemantation}
  \caption{First implementation of the play-off view.}~\label{fig:firstimplementationplayoffview}
\end{figure}

@@

\subsubsection{Arrow section of selected statistic}
This section illustrates a change for a chosen statistic for the selected team
compared with the season before. This should give a visitor more insight into
why a statistic changed over time. The selected team is represented by a circle
in the same way as explained in the play-off view. The change for a statistic
is represented by three arrows:
\begin{itemize}
    \item Arrow on the left pointing towards the circle: indicating the influence of players who joined the team (team member current season, not previous season)
    \item Arrow on the right of the circle: indicating how the team inherent changed (team member this season and previous season)
    \item Arrow on the left pointing away from the circle: indicating the influence of players who left the team (team member previous season, not current season)
\end{itemize}
<figure of the statistics view>
The shirts next to the arrows are the shirts of players that had the biggest 
contribution to that arrow. Note that these shirts don't change in size. The box on 
the right enables the user to change between statistics. Next to that it informs the user of which statistic has been chosen. When the user hits the circle in the middle representing the teams, he is guided to the team view. This view will be explained in more detail in the next section.
<filtering: 
- time \& team
- based on exploration (small multiples)
- dynamically: changes impact multiple parts>

\subsubsection{Small multiples of different statistics}
Below the arrow section small multiples are shown of multiple statistics over time. 
The line charts enables a user to identify peaks or drops that possibly influenced the 
outcome of a team is this season, following seasons or previous seasons. A user interacts with the visualization by shifting the bar indicating the current year displayed. By doing this the view gets updated and the user can see the impact on the team in the context section and why the statistic changes in the arrow section. An alternative to scroll through time is to use the timeline at the bottom of the page.
<this vis helps us comparre statistics over time and relations between them
eg. srs score \& play-off ranking>

@@

\section{Possible improvements}
As with most projects, the result is never 'finished', meaning that there are always improvements possible but due to timing or resource constraints the haven't all been implemented. In what  follows, we suggest a number of features that might improve the visualization:
\begin{itemize}
    \item Smooth transitions between states could improve the user experience. For example when changing year, a transformation of the arrow in the statistics view would help the user see a difference between years.
    At the moment the arrows change at the blink of an eye, making it difficult for us humans with a short term memory to make the comparison.
    \item To further support our short term memory we could also 'save' the previous state. Eg. in the field view we could visualize ghost shirts to indicate which players left the team or position and highlight players that joined the team. 
    This would help the user see how the team changes over time.
    \item At the moment no attention has been payed to the process \& provenance of the exploration. A user thus needs to  memorize his action to be able to share or reproduce his actions. This could be improved by adding URL parameters. This
    way a user at least can share or save a state of an analysis. One step further is to provide a play-feature. The visitor could them share his exploration and replay it. A simple implemention would ask the visitor for a start date and an end date and
    would then 'play' the changes of a particular team and characteristic over time.
    \item We could support users further in exploring for patterns by focussing more on comparisons. We could integrate a view where a visitor is able to compare two teams in the same year, or in two different years.
\end{itemize}
